\textit{Complex Variables and Elliptic Equations} \LaTeX\ guide for authors (Style 2 + NLM reference style)

### 2016-12-22 cvee_paper_gerasimovd.tex
Appropriate references

Also, we'll note two useful facts: TODO REFERENCE HERE FROM TEXT
\begin{itemize}
\item $C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0$
\item $C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r}$, which means that $C - R$ is $\mathcal{O}(\frac{1}{R})$
\end{itemize}

@@

Integral of the second part of the integrand is:
\[
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} = 2 \sqrt{\frac{V}{4} - (C - R)} < 2 \sqrt{\frac{V}{4}} = \mathcal{O}(1)
\]

@@

First, take a look at the multiplier before the integral, it's pretty clear it has order of growth $\mathcal{O}(\frac{1}{\sqrt{R}})$.

@@

It's easy to see that the coefficient before the integral has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

@@

Again, estimating \ref{eq:int_f_up} from above:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
% \\  = & \ln^2 f(y) \mathcal{O}()
\end{align*}

Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$. Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm as well. Finally, we get an expression of order $\mathcal{O} \left( \frac{1}{R} \right) \mathcal{O}( \sqrt R ) = \mathcal{O} \left( \frac{1}{\sqrt{R}} \right)$.

\subsubsection{Final estimate of $\int \left|f(t)\right|^2$}
We split our integration path in five intervals, and the integral has order:
\[
\mathcal{O} \left( \frac{1}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) +\mathcal{O}\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) = \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right)
\]
, which means that integral converges to $0$ as $r$ goes to $1$ and $R$ goes to $\infty$.

>>>>

Also, we'll note two useful facts:
\begin{subequations}
\begin{equation}
C(r) - R(r) = \frac{(1 - r)^2}{1 - r^2} > 0
\label{eq:cr_positive}
\end{equation}
\begin{equation}
C(r) - R(r) = \frac{1 - r}{1 + r} < \frac{1}{R(r)} = \frac{1 - r^2}{2 r} \implies C - R \text{\ is\ } \mathcal{O}\left(\frac{1}{R}\right)
\label{eq:cr_small}
\end{equation}
\end{subequations}

@@

Integral of the second part of the integrand is:
\begin{align*}
\int\limits_{C - R}^{\frac{V}{4}} \frac{1}{\sqrt{R - C + y}} 
   & = 2 \sqrt{\frac{V}{4} - (C - R)} 
\\ & < 2 \sqrt{\frac{V}{4}} && \text{, since $C - R > 0$, see (\ref{eq:cr_positive})}
\\ & = \mathcal{O}(1)
\end{align*}

@@

First, take a look at the multiplier before the integral, using (\ref{eq:cr_small}) it is pretty clear it has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

@@

Using (\ref{eq:cr_small}), it is easy to see that the coefficient before the integral has order of growth $\mathcal{O}\left(\frac{1}{\sqrt{R}}\right)$.

@@

Again, estimating \ref{eq:int_f_up} from above:
\begin{align*}
       & \int \ln^2 f(y) \frac{R}{R^2 - C^2 + 2 (C + 1) y + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ \le & \int \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R + C - y}} \frac{1}{\sqrt{R - C + Z}}
\\ =   & \ln^2 f(C) \frac{R}{R^2 - C^2 + 2 (C + 1) C + 1} \frac{1}{\sqrt{R - C + Z}} \int \frac{1}{\sqrt{R + C - y}}
\end{align*}

Integral $\frac{1}{\sqrt{R + C - y}}$ from $C$ to $C + R$ is elementary and equals $2 \sqrt{R}$. Function $f$ at $C$ is bounded by constants not dependent on $r$, therefore, the square of its logarithm is bounded as well. Finally, we get an expression of order $\mathcal{O} \left( \frac{1}{R} \right) \mathcal{O}( \sqrt R ) = \mathcal{O} \left( \frac{1}{\sqrt{R}} \right)$.

\subsubsection{Final estimate of $\int \left|f(t)\right|^2$}
We have split our integration path in five intervals, and the integral has order:
\[
\mathcal{O} \left( \frac{1}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) +\mathcal{O}\left(\frac{\ln^2 R}{R \sqrt{R}}\right) + \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right) + \mathcal{O} \left( \frac{1}{\sqrt{R}} \right) = \mathcal{O}\left( \frac{\ln^3 R}{\sqrt{R}} \right)
\]
, which means that integral converges to $0$ as $r$ goes to $1$ and $R$ goes to $\infty$.
